---
title: "Certification and Adoption Evaluation Summary"
subtitle: "Session: Screening, Assessing, and Approving: The Certification and Adoption Home Study Process"
date: "Date: September 8, 2021, February 16, 2022, July 6, 2022, and February 22, 2023"


params: 
    cohort: "2123"
    session: "SAA"
    
output: 
     html_document:
       df_print: paged
       fig_width: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache = FALSE)
```

```{r library, include=FALSE}
library(tidyverse)
library(skimr)
library(janitor)
library(ggthemes)
library(hrbrthemes)
library(readxl)
library(ggtext)
library(ggalt)
library(ragg)
library(systemfonts)
library(gt)
library(knitr)
library(pagedown)

```


```{r colors, include=FALSE}
psu_green <- "#6d8d24"
psu_electricgreen <- "#cfd82d"
psu_forestgreen <- "#213921"
psu_blue <- "#008ac1"
psu_lightblue <- "#a5dff9"
psu_sand <- "#e8d3a2"
psu_stone <- "#8a8a67"
psu_yellow <- "#ffc20e"
psu_red <- "#e64927"
psu_orange <- "#f68b1f"
psu_purple <- "#650360"
```

```{r import data, include=FALSE}
ca_session <-read_excel(path = "I:\\Staff\\GSSW\\SALEM\\DATA ENTRY\\Certification Adoption\\Old\\Certadopt 21-23.xlsx",
                                   sheet = "Data") %>% 
  clean_names() %>% 
  mutate(date = as.character(date)) %>% 
  mutate(cohort = recode(cohort, "202109" = "2123",
                              "202202" = "2123",
                              "202207" = "2123",
                              "202302" = "2123"))

```


```{r import registered, include=FALSE}
ca_registered <- read_excel(path = "I:\\Staff\\GSSW\\SALEM\\DATA ENTRY\\Certification Adoption\\Old\\Certadopt 21-23.xlsx",
                                   sheet = "Registered") %>% 
  clean_names() 
```

```{r, include=FALSE}
number_of_respondents <- ca_session %>% 
  filter(cohort == params$cohort,
         session == params$session) %>% 
  count(cohort) %>% 
  pull(n)
```


```{r, include=FALSE}
number_registered <- sum(ca_registered$registered) 
```

| Respondents: **`r number_of_respondents`**  
| Registered: **`r number_registered`** 
| Response Rate*:  **`r scales::label_percent()(number_of_respondents/number_registered)`**
|                       *does not account for makeups or absences


```{r knowledge-mean}

ca_know_mean <- ca_session %>%
  select(cohort,session, pre_kno,post_kno) %>% 
  group_by(cohort,session) %>%
  summarize(before = mean(pre_kno, na.rm = TRUE),
            after = mean(post_kno, na.rm = TRUE)) %>% 
  ungroup()%>% 
 mutate(before = round(before,1),
        after = round(after,1)) %>% 
  pivot_longer(cols = -c(cohort, session),
               names_to = "time",
               values_to = "mean",
               values_drop_na = TRUE)

```


|
|
|


```{r prepost-graph, fig.height = 3}
ca_know_mean %>% 
  filter(session == params$session,
         cohort == params$cohort) %>% 
  drop_na() %>%
  ggplot(aes(x = mean,
             y = time,
             fill = time,
             label = mean)) +
  geom_col(show.legend = FALSE) +
  geom_text(family = "URWGothic", color = "black",
            hjust = 1.5, size = 5) +
  scale_fill_manual(values = c(
                     "before" = psu_lightblue,
                     "after" = psu_blue)) +
  scale_x_continuous(expand = expansion(add = c(0,0.1)), labels = NULL) +
  scale_y_discrete(expand = expansion(add = 0.1)) +
  labs(title = "Participant Self Assessed Knowledge Gained") +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown())


```
 

```{r scale questions, include=FALSE}
ca_scales <- ca_session %>%
  select(cohort,session,tr_know,learn_ob,content,material,interaction) %>% 
  group_by(session, cohort) %>%
  mutate(tr_know = factor(case_when(
    tr_know == "5" ~ "Agree",
    tr_know == "4" ~ "Somewhat Agree",
    tr_know == "3" ~ "Neutral",
    tr_know == "2" ~ "Somewhat Disagree",
    tr_know == "1" ~ "Disagree",
    TRUE ~ NA_character_))) %>% 
  mutate(learn_ob = factor(case_when(
    learn_ob == "5" ~ "Agree",
    learn_ob == "4" ~ "Somewhat Agree",
    learn_ob == "3" ~ "Neutral",
    learn_ob == "2" ~ "Somewhat Disagree",
    learn_ob == "1" ~ "Disagree",
    TRUE ~ NA_character_))) %>%
  mutate(content = factor(case_when(
    content == "5" ~ "Agree",
    content == "4" ~ "Somewhat Agree",
    content == "3" ~ "Neutral",
    content == "2" ~ "Somewhat Disagree",
    content == "1" ~ "Disagree",
   TRUE ~ NA_character_))) %>% 
  mutate(material = factor(case_when(
    material == "5" ~ "Agree",
    material == "4" ~ "Somewhat Agree",
    material == "3" ~ "Neutral",
    material == "2" ~ "Somewhat Disagree",
    material == "1" ~ "Disagree",
    TRUE ~ NA_character_))) %>%          
  mutate(interaction = factor(case_when(
    interaction == "5" ~ "Agree",
    interaction == "4" ~ "Somewhat Agree",
    interaction == "3" ~ "Neutral",
    interaction == "2" ~ "Somewhat Disagree",
    interaction == "1" ~ "Disagree",
   TRUE ~ NA_character_))) %>%
ungroup() %>% 
  pivot_longer(cols = -c(cohort, session),
               names_to = "scale",
               values_to = "rating",
               values_drop_na = TRUE) %>% 
  count(cohort, session, scale, rating) %>% 
  group_by(cohort, session, scale) %>% 
  mutate(pct = n / sum(n))
```

\newpage

### Scale Ratings
 - **Trainer** demonstrated knowledge in content presented
 - **Learning objectives** were covered
 - **Content** was applicable to job
 - **Materials** and Handouts were helpful
 - There was a sufficient amount of **interaction** to keep engaged


```{r}
ca_scales %>%
  filter(session == params$session,
         cohort == params$cohort) %>%
  drop_na() %>%
  ungroup() %>%
  mutate(rating = fct_relevel(rating, c("Agree",
                     "Somewhat Agree",
                     "Neutral",
                     "Somewhat Disagree",
                     "Disagree")),
         rating = fct_explicit_na(rating, na_level = "(missing")) %>% 
  mutate(scale_name = case_when(scale == "interaction" ~ "Interaction",
                                scale == "learn_ob" ~ "Learning Objectives",
                                scale == "material" ~ "Materials",
                                scale == "tr_know" ~ "Trainer",
                                scale == "content" ~ "Content",
                                TRUE ~NA_character_)) %>%
  ggplot(aes(x = pct,
             y = rating,
             fill = rating)) +
    scale_fill_manual(values = c(
                     "Agree" = psu_green,
                     "Somewhat Agree" = psu_electricgreen,
                     "Neutral" = psu_sand,
                     "Somewhat Disagree" = psu_yellow,
                     "Disagree" = psu_orange)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = scales::percent(pct, accuracy = 1)),
            color = "black",
            hjust = 0,
            size = 3) +
  scale_x_continuous(expand = expansion(add = c(0,0.1)), labels = NULL) +
  scale_y_discrete(expand = expansion(add = 0.1)) +
  facet_wrap(~scale_name) +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown())


```

\newpage
### Participant Comments

```{r}
 ca_session %>%
  filter(session == params$session,
         cohort == params$cohort) %>%
   select(liked_best) %>%
  drop_na()  %>% 
  gt() %>% 
  tab_options(table.align = "left") %>%
  cols_label(
    liked_best = md("**Liked Best**"))
  
```


```{r}
ca_session %>%
  filter(session == params$session,
         cohort == params$cohort) %>% 
  select(to_improve) %>% 
  drop_na() %>% 
  gt() %>% 
  tab_options(table.align = "left") %>%
  cols_label(
    to_improve = md("**To Improve**"))
  
```